---
title: "R Notebook"
output: html_notebook
---


```{r}
library(C50)
library(caret)
library(rpart)
```

Reading the data and assigning it to a variable
```{r}

tabA <- read.csv("TABULAR_A.csv")
tabB <- read.csv("TABULAR_B.csv")

```

Displaying first 3 row from tabA 
```{r}

head(tabA,n = 3)

```

Displaying last 3 rows from tabA
```{r}

tail(tabB,n = 3)

```

loading sqldf library
```{r}
library(sqldf)
```

Query and find each count in car_rank category
```{r}
sqldf("select car_rank, count(*) as tot from tabA group by car_rank order by tot desc")

```

Leftouter join with tabB and find the category
```{r}
sqldf("select a.car_rank, count(*) as tot from tabA as a left outer join tabB as b  on a.owner_id = b.owner_id group by a.car_rank order by tot desc")

```

find the duplicates of owner_id in tabB
```{r}

sqldf("SELECT owner_id, COUNT(*) count FROM tabB GROUP BY owner_id HAVING count > 1")

```

Segmenting tht tabA with 3 clusters
```{r}

set.seed(21)
tabACluster <- kmeans(tabA[, 2:7], 3,nstart = 20)
tabACluster

plot(tabA[, 2:7], col =(tabACluster$cluster +1) , main="K-Means result with 3 clusters", pch=20, cex=2)



```


Comparing the cluster obtained with car_rank distribution
```{r}

table(tabACluster$cluster, tabA$car_rank)

```
Converting the cluster label to factor variable

```{r}

clust <- as.factor(tabACluster$cluster)

```


Merging the cluster label with the tabA

```{r}

tabA <- cbind(tabA,clust)

str(tabA)

```

Segregating the data based on their cluster obtained
```{r}

tabA_1 = tabA[with(tabA, clust == "1" ),]

tabA_2 = tabA[with(tabA, clust == "2" ),]

tabA_3 = tabA[with(tabA, clust == "3" ),]

```


comparing the distribution of data across cluster and car_rank
```{r}

table(tabA_1$clust, tabA_1$car_rank)

table(tabA_2$clust, tabA_2$car_rank)

table(tabA_3$clust, tabA_3$car_rank)


```


*****************************************************************************
Cluster 1: The car_rank contains two class
Cluster 2: The car_rank contains only one class
Cluster 3: The car_rank contains all 4 class
******************************************************************************

-------------------------------
Modeling 
-------------------------------


Spliting data to train and test
Function to re-use the code on each clusters
```{r}

splitData <- function(x){
# Divide the data into test and train
set.seed(123)

train_RowIDs = sample(1:nrow(x), nrow(x)*0.7)
train_Data = x[train_RowIDs,]
test_Data = x[-train_RowIDs,]

dataList<- list("train"= train_Data, "test"= test_Data) 


return(dataList)

rm(train_RowIDs)
}

```

Spliting on cluster 1 and 3 data
```{r}

tabA_1_split <- splitData(tabA_1)

tabA_3_split <- splitData(tabA_3)

```

Modeling using Decision tree with rpart function

```{r}

decisionTree_rpart <- function(dataf){
dtCart=rpart(car_rank~car_price + maint_cost + num_doors + person_capacity + trunk_size + safety_rating, data=dataf$train, method="class")    

#Ploting the decision graph
plot(dtCart,main="Classification Tree for Car Rank Class",margin=0.15,uniform=TRUE)
text(dtCart,use.n=T)
#Summarizing the rules
summary(dtCart)

#Predict in train data
print("Train Error Metrics")

ctrain = table(dataf$train$car_rank, predict(dtCart, newdata=dataf$train, type="class"))

ctrain_confusion <- confusionMatrix(ctrain)
print(ctrain_confusion)
#predict in test data
ctest=table(dataf$test$car_rank, predict(dtCart, newdata=dataf$test, type="class"))

print("Test Error Metrics")
ctest_confusion <- confusionMatrix(ctest)
print(ctest_confusion)
}

```

Running the decision tree on cluster 1 data
```{r}

decisionTree_rpart(tabA_1_split)

print("Train Accuracy is 96")
print("Test Accuracy is 97")
```
Running the decision tree on cluster 3 data

```{r}
decisionTree_rpart(tabA_3_split)
print("Train Accuracy is 90")
print("Test Accuracy is 85")

```

Modelbuilding using Decision Tree using C5.0


Wrinting function to reuse
```{r}

decisionTree_C5 <- function(dataf){
dtC50 = C5.0(car_rank~car_price + maint_cost   + trunk_size + safety_rating, data = dataf$train, rules=TRUE)

#summarize the rules
summary(dtC50)


#predicting the train data
ctrain = table(dataf$train$car_rank, predict(dtC50, newdata=dataf$train, type="class"))
print("Train Error Metrics")
ctrain_confusion <- confusionMatrix(ctrain)
print(ctrain_confusion)

#predicting the test data
ctest=table(dataf$test$car_rank, predict(dtC50, newdata=dataf$test, type="class"))
print("Test Error Metrics")
ctest_confusion <- confusionMatrix(ctest)
print(ctest_confusion)

}

```


Running the decision tree on cluster 1 and 3 data
```{r}
decisionTree_C5(tabA_1_split)

decisionTree_C5(tabA_3_split)


```
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
